%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Malik Salvosa 09/2018 %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper]{altacv}

%Layout
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

%Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}
\usepackage{siunitx}

%Colors

\definecolor{accent}{HTML}{000e17}
\definecolor{heading}{HTML}{000e17}
\definecolor{emphasis}{HTML}{696969}
\definecolor{body}{HTML}{01415f}

\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{emphasis}
\colorlet{body}{body}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%

\begin{document}
\name{Malik Salvosa}
\tagline{2A Mechatronics Engineering}
\personalinfo{
  \email{mrsalvosa@gmail.com}
  \phone{+1 (647) 524 6743}
  \mailaddress{135 MORAY AVE, Richmond Hill, ON L4E3E2}
  \linkedin{linkedin.com/in/malik-salvosa-bb4071111/}
  \github{github.com/malik0411}
}

%

\begin{fullwidth}
\makecvheader
\end{fullwidth}

%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page1sidebar]{Experience}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Mechanical Engineer}{Skyjack Inc, a Linamar Company}{May 2018 -- August 2018}{}

\begin{itemize}
\item Designed varying complexity carts, fixtures, paint windows, carriers \& racks using SolidWorks, AutoCAD, eDrawings, \& GD\&T.
\item Enhanced project management skills by completing 12+ projects.
\end{itemize}

\textbf{Key achievement:} Designed \& implemented a single cart assembly + two fixtures capable of transporting the 46/63 AJ machine booms + risers.

\divider
%

%%%%%%%%%%%%%
%Experience 2
%%%%%%%%%%%%%

\cvevent{Intern}{The STEAM Project}{July 2017}{}

\begin{itemize}
  \item Assisted councilors in managing the campers' daily activities.
  \item Utilized VEX Robotics, TinkerCAD, and constructed simple structures.
\end{itemize}

\divider
%

%%%%%%%%%%%%%
%Experience 3
%%%%%%%%%%%%%

\cvevent{Instructor}{Ascension Jiu-Jitsu Academy}{April 2012 -- June 2017}{}

\begin{itemize}
  \item Responsible for instructing classes to aid in student development.
  \item Improved organizational skills by managing curriculum and evaluation.
\end{itemize}

\medskip

%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Design Team %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page2sidebar]{Design Team}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Waterloo Formula Electric}{Accumulator Core Member}{September 2018 -- PRESENT}{}

\begin{itemize}
\item Designed and constructed the 72 groupings of 4-cell batteries.
\item Collaborated with the team lead to ensure the timely completion of the remaining cells for the term, after which I aided Aerodynamics.
\end{itemize}

\divider
%

\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page2sidebar]{Projects}

%%%%%%%%%%%%%
%Project 1
%%%%%%%%%%%%%

\cvevent{Chip Sorting Robot}{Programmed in C}{November 2017}{}

\begin{itemize}
  \item Mobile robot constructed using LEGO EV3 parts (ARM9 CPU).
  \item Capable of sorting chip bags (by colour) into predetermined locations, allow users to choose a sorted chip bag, and retrieve the chosen bag.
\end{itemize}

\divider

%

%%%%%%%%%%%%%
%Project 2
%%%%%%%%%%%%%

\cvevent{Robotic Arm}{LEGO Tetrix}{October 2017}{}

\begin{itemize}
  \item Controlled used Servo Motors rotating at \ang{180} and \ang{360}.
  \item Utilized hydraulics to improve its' range of motion.
  \item Capable of retrieving small objects and placing them in receptacles.
\end{itemize}

\end{document}